Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-20 talk/iwtc11/paper.tex
fix XXX

The loop peeling optimization was implemented in the PyPy
framework. That means that the JIT-compilers generated for all
interpreters implemented within PyPy now can take advantage of
it. Benchmarks have been executed for a few different interpreters and
we see improvements in several cases. The ideal loop for this optimization
would be short numerical calculations with no failing guards and no
external calls.

XXX reason why we use small numerical kernels for benchmarks

>>>>

The loop peeling optimization was implemented in the PyPy
framework. That means that the JIT-compilers generated for all
interpreters implemented within PyPy now can take advantage of
it. Benchmarks have been executed for a few different interpreters and
we see improvements in several cases. The ideal loop for this optimization
would be short numerical calculations with no failing guards and no
external calls. Larger loops involving many operations on complex objects
typically benefit less from it. Loop peeling never makes performance worse, in
the worst case the peeled loop is exactly the same as the preamble. Therefore we
chose to present benchmarks of small numeric kernels where loop peeling can show
its use.
